Towards a Complete Model of Mutation Selection Balance in Humans

### 2023-05-13 manuscript/manuscript.tex
more theory

(c.f. \cite{Robertson1961-ho,Santiago1995-hx}; see XXX for a proof).

Note that assuming $V^2=2$.

are subtle differences in the effective population sizes

This is often
expressed as rescaling the effective population size by

>>>>

(c.f. \cite{Robertson1961-ho,Santiago1995-hx}; see XXX for a proof). Note that
this assumes the usual Wright--Fisher non-heritable variance, i.e. $V^2=2$.
However, because the autocorrelation in allele frequency builds up each
generation relative to the fitness background its on, the inflation term $Q^2$
has a temporal dimension. For notational efficiency, we assume $Q^2$ refers to
the asymptotic $Q_t^2$ as $t \to \infty$ and we consider the \emph{asymptotic}
$N_e$ created by draft. In general, however, statistics such as heterozygosity
depend on the cumulative autocorrelation factor \emph{up to some time} $t$,
$Q_t^2$ \parencite[p. 2111]{Santiago1998-bs}. This reflects the fact that
effective population size experienced by a mutation newly associated with a
fitness background is larger than the asymptotic effective population size,
since not much autocorrelation has accumulated in the stochastic perturbations
caused by drift yet.
